Existence of Forward Simulations for Particular Data Structures

### 2017-01-11 draftCAV/app-backSim.tex
in principle, finished the preliminaries

\begin{lem}
Let $L_1$ and $L_2$ be two libraries over a common alphabet $\Sigma$. $L_1$ refines $L_2$ if{f} there exists a backward simulation from $L_1$ to $L_2$.
\end{lem}
\begin{proof}
Looks trivial and follows Lynch paper. Can be completed later.
\end{proof}

>>>>

\begin{lem}
Let $L_1$ and $L_2$ be two libraries over a common alphabet $\Sigma$, and $\Gamma\subseteq \Sigma$ a set of actions such that $(C\cup R)\subseteq \Gamma$. $L_1$ $\Gamma$-refines $L_2$ if{f} there exists a $\Gamma$-backward simulation from $L_1$ to $L_2$.
\end{lem}
\begin{proof}
Looks trivial and follows Lynch paper. Can be completed later.
\end{proof}
